%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Navya}{Dundi}{ \urlstyle{same}\\
\href{mailto:navyad@gmail.com}{navyad@gmail.com}\\ \href{mailto:0000000@svecw.edu.in}{000000@svecw.edu.in} |  
\href{tel:+911234567890}{+91 1234567890    } 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Shri Vishnu Engineering}
\subsection{College for Women}
\descript{Btech in Computer Science}
\location{CGPA : 8.9 \\2022 - ongoing | Bhimavaram, Andhra Pradesh, India}
\sectionsep

\subsection{ABCDE college}
\descript{MPC |  percentage : 82.8\%}
\textbf{BIEAP}\\
\location{2020 - 2022 | XYZ, Andhra Pradesh, India}


\sectionsep

\subsection{ADC High School}
\descript{percentage : 96.6\%}
\textbf{BSEAP}\\
\location{May 2020|  xyz, Andhra Pradesh, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Leetcode://
\href{https://leetcode.com/navyadundi/}{\bf navyadundi}\\
GitHub://
\href{https://github.com/navyadundi}{\bf navyadundi}\\
Smart Interviews:// \href{https://smartinterviews.in/profile/navyadundi}{\bf navyadundi} \\
Codechef://  \href{https://www.codechef.com/users/navyadundi}{\bf navyadundi} \\
Hacker Rank://
\href{https://www.hackerrank.com/profile/navyadundi}{\bf navyadundi}\\
LinkedIn://  \href{https://www.linkedin.com/in/navyadundi/}{\bf navyadundi} \\

\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\sectionsep
\subsection{Programming Languages}

\textbullet{Java} \\
\textbullet{Basics in C}


 \subsection{Technologies}
\textbullet{HTML}\\
\textbullet{CSS}\\
\textbullet{React.js}\\
\textbullet{SQL}\\
\textbullet{Database Management System}\\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Soft Skills}

\textbullet{Communication Skills}\\
\textbullet{Team Management}\\
\textbullet{Self-Motivated\\}
\textbullet{Adaptable}


\section{PERSONAL INTERESTS}

\textbullet{Photo Editing}\\
\textbullet{Video Editing}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



\section{project}
\runsubsection{full-stack eCommerce website using the MERN Stack}\\
\location{}
\begin{tightemize}

\item Utilized React.js to create an interactive and responsive user interface, ensuring a seamless user experience.\\
\item For the backend we want to develop a scalable backend infrastructure using Express.js and Node.js.\\
\item Incorporating MongoDB as the database solution for efficient data storage and retrieval.

\descript{Technologies used:}
\textbullet{Front-end: React.js\\
\textbullet{Back-end: Node.js, Express.js}\\
\textbullet{Database: MongoDB}
}
\end{tightemize}
\sectionsep


\runsubsection{TaskTide – Productive Tools Application  | }\href{https://}{Link}
\location{}
\begin{tightemize}

\item Developed a comprehensive productivity application designed to enhance user's time and task management effectively. \\
\item TaskTide combines essential productivity tools, including a To-Do List, Notes,
Timer, and Event Calendar, into a single comprehensive platform.
\item The application offers an intuitive user interface and ensures seamless user experience through responsive design and robust functionality.
\descript{Technologies used:}
\textbullet{Front-end: HTML, CSS, JavaScript, Bootstrap\\
\textbullet{Database: Firebase Realtime Database}\\
\textbullet{Version Control: Git and GitHub}\\

}
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep
\section{Co-Curricular Activites}

\runsubsection{Coding Contest ||}\href{}{Link}
\descript{ TOP-50 CODERS- CODING EXTRAVAGANZA \location{December-2022}}


\begin{tightemize}
\item Participated in College Level Contest Coding Extravaganza. I listed in the \textbf{TOP 50 Coders }solving problems using C programming language.
\end{tightemize}


\runsubsection{Technical Poster Presentation}

\descript{ Poster Design \& Presentation Winners 
\location{April 2023}}

\begin{tightemize}
\runsubsection{}
\item I led a team of two enthusiasts. Our collective effort centered on the theme of Nanotechnology, showcasing innovative concepts and advancements in the field.
\item Our team's presentation garnered significant recognition, culminating in us securing the \textbf{FIRST} place in the competition.
\end{tightemize}
\sectionsep

\runsubsection{Group Discussion}

\descript{  Tech League \location{May 2023}}

\begin{tightemize}
\runsubsection{}
\item I participated in the event Tech League (Group discussion) which is conducted College level among the 40-50 participants.
\item I got \textbf{Second place} in the event Tech League.
\end{tightemize}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\section{Certifications} 
\subsection{}

\begin{tightemize}

\item Database Programming with SQL \textbf{-ORACLE} \href{}{Link}\location{2024}
\item Google AI for Anyone 
 (EDX) \textbf{-GOOGLE}\location{June 2024}
 
 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
